Satellite Alignments in the Local Group

### 2017-07-10 paper/paper.tex
plane width + table with interesting quantities

We compute the cosmic web from the DM information in the
Illustris-3 simulation which share the same structure information with
Illustris-1 on scales of $1$ \Mpc.  
Illustris-3 has $455^3$ DM particles, corresponding to
$4.0\times 10^8$ \Msun in DM particle mass and $5.7$ kpc for the DM
gravitational softwning lentgh.

@@

\begin{itemize}
\item {\bf Stellar mass}. LGA galaxy pairs are composed by galaxies with stellar mass in the
range $1\times10^{10}\Msun <M_{\star}<1.5 \times 10^{11} \Msun$.
\item {\bf Dominant pairs}. For each galaxy $A$ we find its closest galaxy $B$, if galaxy $A$ is also
the closest to halo $B$, the two halos are considered as a pair. 
Another way to phrase this selection is that pairs do not have
neighbors closer than the pair's distance.
\item {\bf Separation}. The distance between the galaxies' center of
  mass must be in the range $500$ kpc $<d_{AB}<$ $1500$ kpc. 
\item {\bf Isolation}. For each galaxy in the pair there cannot be a galaxy more
  massive than the lightest galaxy in the pair within a radius of $2$
  Mpc. 
\end{itemize}

@@

We characterize the satellite spatial distribution in two ways. 
First, by computing the inertia tensor defined as

@@

@@

>>>>

We compute the cosmic web from the DM information in the
Illustris-3 simulation which share the same structure information with
Illustris-1 on scales of $1$ \Mpc.  
Illustris-3 has $456^3$ DM particles, corresponding to
$4.0\times 10^8$ \Msun in DM particle mass and $5.7$ kpc for the DM
gravitational softwning lentgh.

@@

\begin{itemize}
\item {\bf Stellar mass}. LGA galaxy pairs are composed by galaxies with stellar mass in the
range $1\times10^{10}\Msun <M_{\star}<1.5 \times 10^{11} \Msun$.
\item {\bf Dominant pair}. For each galaxy $A$ we find its closest galaxy $B$, if galaxy $A$ is also
the closest to halo $B$, the two halos are considered as a pair. 
Another way to phrase this selection is that pairs do not have
neighbors closer than the pair's separation.
\item {\bf Separation}. The distance between the galaxies' center of
  mass must be in the range $500$ kpc $<d_{AB}<$ $1500$ kpc. 
\item {\bf Isolation}. For each galaxy in the pair there cannot be a galaxy more
  massive than the lightest galaxy in the pair within a radius of $2$
  Mpc. 
\end{itemize}

@@

We characterize the bright ($M_V<-9$) satellite spatial distribution
with four different metrics.

\begin{enumerate}
\item{The inertia tensor}.
\item{Fitting planes}.
\item{Velocity Anisotropy}.
\item{Alignment with the cosmic web}. 
\end{enumerate}

I what follows we describe the details of implementation of each
metric.

\subsection{Inertia Tensor}
\label{sub:inertia}
First, by computing the inertia tensor defined as

@@

\subsection{Plane fitting}
\label{sub:planes}

We fit satellite planes around each galaxy in the pair by randomly
generating 10000 unit vectors over the  sphere, each vector
representing the direction perpendicular to a plane passing through
the main galaxy's center of mass. 
We compute the dot product of the unit vector with the position vector
for each satellite, this scalar gives us the satellite distance to the
plane. 
The best plane is determined by the vector that gives the lowest
position satellite distance dispersion. 
We take the dispersion value as a measure of the plane's width.
For comparison we also store the value and direction giving the
highest distance dispersion.

\subsection{Velocity Anisotropy}
\label{sub:beta}

The velocity anisotropy paramenter, $\beta$ is defined as

\begin{equation}
  \beta = 1 - \frac{\sum_i v^2_{\rm{tan}; i}}{2\sum_i v^{2}_{\rm{rad};i}},
\label{eq:beta}
\end{equation}
% 
where $v_{\rm{tan/rad};i}$ correspond to the tangential/radial
velocity of the $i$-th satellite with respect to the central galaxy.

\begin{table*}
  \centering
\begin{tabular}{lll}
\hline\hline
Symbol & Units & Description\\\hline
$M_{\star}$ & $10^{10}$\Msun & Stellar mass\\
$N_s$ & & Number of satellites with $M_V<-9$\\
$a > b> c$ & & Inertia tensor eigenvalues. \\
$\hat{s}_1$, $\hat{s}_2$, $\hat{s}_3$ & & Inertia tensor eigenvectors. \\
$\beta$  &  & Satellite Velocity Anisotropy\\
$\sigma_s$ & kpc & Plane width\\
$\lambda_1>\lambda_2>\lambda_3$ &  & Hessian Matrix
eigenvalues\\
$\hat{e}_{1}$,  $\hat{e}_{2}$,  $\hat{e}_{3}$ & - & Hessian Matrix
eigenvectors\\ 
$\hat{r}_{AB}$& & Unit vector in the direction to the galaxy companion\\

\hline\hline
\end{tabular}
  \caption{Overview of the parameters computed for each central galaxy
    and its satellite system.
  \label{tab:models}}
\end{table*}

@@

%% Alignments between galaxies, satellite systems and haloes
%% https://arxiv.org/pdf/1605.01728.pdf

%% The tangential velocity excess of the Milky Way satellites
%% https://arxiv.org/pdf/1612.01529.pdf
